\documentclass[10pt]{article}
\usepackage[a4paper,margin=1.8cm]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{caption}
\usepackage{float}
\setlength{\parskip}{3pt}
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.08}
\title{Supplementary Evidence for\\Explainable Early Warning for Next-Week Abnormal Reported 311 Demand}
\author{}
\date{}
\begin{document}
\maketitle
\noindent This supplement is generated from the repository's current stored artifacts. The final comparison uses the T2 event: a shifted eight-week abnormality and next-week count at least three. Unless stated otherwise, the final protocol trains through 2023, selects calibration and thresholds on 2024, and evaluates unchanged on held-out 2025 rows.

\section*{S1. Historical-volume performance}
Train-derived cut points of the shifted eight-week historical mean define the volume groups; no test label is used to form the groups. Repeated zero-valued cut points collapse the nominal deciles to nine observable bins. All rows below sum to the full held-out 2025 T2 population.
\begin{table}[H]
\centering\scriptsize
\input{tables/supplementary/volume_deciles.tex}
\caption{Final Platt-calibrated LightGBM performance by train-derived historical-volume group on held-out 2025 T2 rows.}\label{tab:supp-volume}
\end{table}
\clearpage

\section*{S2. Complaint-category mapping and residual category}
\begin{table}[H]
\centering\small
\input{tables/supplementary/complaint_mapping.tex}
\caption{Deterministic mapping of original 311 complaint types to the nine analysis categories.}\label{tab:supp-mapping}
\end{table}
\begin{table}[H]
\centering\small
\input{tables/supplementary/other_composition.tex}
\caption{Largest original complaint types in the residual \texttt{other} category.}\label{tab:supp-other}
\end{table}
\clearpage

\section*{S3. Same-target baseline comparison}
Every row uses the same held-out 2025 T2 population. Formula-threshold decisions apply the T2 threshold to predicted counts; the LightGBM threshold is selected on validation 2024.
\begin{table}[H]
\centering\scriptsize
\input{tables/supplementary/same_target_baselines.tex}
\caption{Full baseline metrics on the shared T2 task.}\label{tab:supp-baselines}
\end{table}
\clearpage

\section*{S4. Bootstrap uncertainty and seed stability}
Baseline intervals use 250 NTA-category cluster resamples; the main LightGBM confidence intervals reported in the manuscript use 1,000. The reported estimate is the held-out 2025 value; this table does not turn distinct decision rules into a single superiority claim.
\begin{table}[H]
\centering\scriptsize
\input{tables/supplementary/baseline_bootstrap_ci.tex}
\caption{Cluster-bootstrap uncertainty for final-comparison rows.}\label{tab:supp-bootstrap}
\end{table}
\begin{table}[H]
\centering\small
\input{tables/supplementary/seed_stability.tex}
\caption{Five-seed held-out stability for key ablation configurations. Values are mean $\pm$ standard deviation.}\label{tab:supp-seeds}
\end{table}
\clearpage

\section*{S5. Chronological, calibration, and target-sensitivity evidence}
\begin{table}[H]
\centering\small
\input{tables/supplementary/rolling_origin.tex}
\caption{Expanding-window rolling-origin test metrics for T2.}\label{tab:supp-rolling}
\end{table}
\begin{table}[H]
\centering\small
\input{tables/supplementary/calibration.tex}
\caption{Final-style 2025 calibration diagnostics for T2.}\label{tab:supp-calibration}
\end{table}
\noindent The following is a labelled 2024--2025 target-definition diagnostic, not the same-task baseline comparison in Section S3.
\begin{table}[H]
\centering\small
\input{tables/supplementary/target_sensitivity.tex}
\caption{Target-sensitivity diagnostic with prevalence and ranking metrics.}\label{tab:supp-targets}
\end{table}

\section*{S6. Count-model limitation}
Poisson GLM fits converged within the configured 500 iterations. A Negative Binomial GLM is not included because \texttt{statsmodels} was unavailable in the recorded environment and scikit-learn does not provide a Negative Binomial GLM. This is a documented tooling limitation, not an omitted result.
\end{document}
